Decentralised Authoring, Annotations and Notifications for a Read-Write Web with dokieli

### 2017-04-07 index.tex
formatting

\par dokieli is open source: \url{https://github.com/linkeddata/dokieli} and available to try at \url{https://dokie.li/} (or at any instance on the Web, see \empty Adoption).

>>>>

\par dokieli is open source (\url{https://github.com/linkeddata/dokieli}) and available to try at \url{https://dokie.li/} (or at any instance on the Web, see \empty Adoption).
